---
title: 'Pretzel preprint title'
author:
- Author First (University of Foo)
- Another Person (University of Bar)
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: false
abstract: 
  This is the abstract.
bibliography: references.bib
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "figures/"
)
```



# Introduction

Cite papers like this: `[@jimnez2017]` [@jimnez2017] matching entries in `references.bib`


# Results

You can also include plot, as illustrated in the text below which generates Figure 1. Note that when using `bookdown::pdf_document2` as the output (as illustrated in the example YAML code above) the syntax `\@ref(fig:basic-plot)` can be used to refer to plots with *automatic numbering*, e.g. Figure \@ref(fig:basic-plot).

```{r basic-plot, fig.cap="A basic plot."}
plot(matrix(rpois(n = 2e3, lambda = 9), ncol = 2))
```

# Acknowledgements {-}

[https://github.com/Robinlovelace/rmarkdown-paper-repo](https://github.com/Robinlovelace/rmarkdown-paper-repo)

# References

